Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\ \begin{large} Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity \end{large}

### 2016-12-17 draft.tex
.

>>>>

Sweeney et al. found that diffusive homeostasis maintains broadness of firing rates across a wide range of diffusion constants but rapidly approaching zero for small values \cite[p. 6]{Sweeney_Paper}. We were able to reproduce this result, see Figure \ref{Fir_Rate_Dist_Width_vs_D}. Homeostasis reaches a point of saturation, where faster diffusion has no effect on the heterogeneity of firing rates. 
\begin{figure}
%%% freq_dist_width_vs_D.py
\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/std_dev_vs_D_neumann.png}
\caption{Standard deviation of firing rate distribution of excitatory neurons (neumann boundary conditions).}
\label{Fir_Rate_Dist_Width_vs_D}
\end{figure}
To further quantify this dependence, we also investigated the influence of the diffusion constant onto the distribution's skewness, shown in Figure \ref{Fir_Rate_Dist_Skew_vs_D}. Compared to the standard deviation, we see a similar but not as clear trend with a drop for very small diffusion constants, even occasionally resulting in a left-skewed distribution (negative D-values).
\begin{figure}
%%% freq_dist_skew_vs_D.py
\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/skew_vs_D_neumann.png}
\caption{Skewness of firing rate distribution of excitatory neurons (neumann boundary conditions).}
\label{Fir_Rate_Dist_Skew_vs_D}
\end{figure}

!!!HEAD!!!
